---
title: "R Notebook"
output: html_notebook
---


```{r}

df <- read.csv("C:\\Users\\Utilisateur\\Downloads\\features_1024tanh.csv")
head(df)


```

```{r}

library(FactoMineR)
df[, 2:1025]


resultats_acp <- PCA(df[, 2:1025], ncp=200, scale.unit = TRUE)

```


```{r}
?PCA

eigenvalues <- resultats_acp$eig

ncol(resultats_acp$var$coord)

premieres_variables_principales <- resultats_acp$ind$coord[, 1:200]

premieres_variables_principales
```
```{r}

colnames(df[, 1000:1027])

identifiants <- df[, c("surveyId", "type")]

donnees_combinees <- cbind(identifiants, premieres_variables_principales)

write.csv(donnees_combinees, "C:\\Users\\Utilisateur\\Downloads\\ACP_features.csv", row.names = FALSE)


```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
